\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2021-10-20 doc/USER_MANUAL/02_getting_started.tex
Update manual about cluster version issue
Update manual about dynamic fault config parameters

>>>>

Beware that some cluster systems that run a recent version many not run and\slash compile an older version of the code. \\

When using dynamic fault in parallel with the developer version, we suggest you to set the configuration parameters 
of {\texttt{FAULT_DISPL_VELOC}} and {\texttt{FAULT_SYNCHRONIZE_ACCEL}} as {\texttt{.true.}}.\\
